Download, Compile and Link OpenBLAS Library with R

### 2020-12-16 README.Rmd
Update site.
Update website.
Update website
Update size logo

@@

<img src="https://raw.githubusercontent.com/prdm0/ropenblas/master/logo.png" height="270" width="250" align="right" />

@@

```{r, fig.align='center',  echo=FALSE}
knitr::include_graphics(path = "inst/asciicast/ropenblas.svg")
```

@@

```{r, echo=FALSE}
knitr::include_graphics(path = "inst/asciicast/last_version_r.svg")
```

@@

```{r, echo=FALSE}
knitr::include_graphics(path = "inst/asciicast/last_version_openblas.svg")
```

@@

```{r, echo=FALSE}
knitr::include_graphics(path = "inst/asciicast/rcompiler.svg")
```

@@

```{r, echo=FALSE}
knitr::include_graphics(path = "inst/asciicast/link_again.svg")
```

>>>>

**ropenblas** 
<a href='logo.png'><img src='logo.png' align="right" height="175" /></a>

@@

<br/><br/><br/>

<!-- <img src="https://raw.githubusercontent.com/prdm0/ropenblas/master/logo.png" height="270" width="250" align="right" /> -->

@@

```{r, fig.align='center',  echo=FALSE}
knitr::include_graphics(path = "https://raw.githubusercontent.com/prdm0/ropenblas/bce920c05f8daa13fc6568e6797d4b841e9d43ce/img/asciicast/ropenblas.svg")
```

@@

```{r, echo=FALSE}
knitr::include_graphics(path = "https://raw.githubusercontent.com/prdm0/ropenblas/bce920c05f8daa13fc6568e6797d4b841e9d43ce/img/asciicast/last_version_r.svg")
```

@@

```{r, echo=FALSE}
knitr::include_graphics(path = "https://raw.githubusercontent.com/prdm0/ropenblas/bce920c05f8daa13fc6568e6797d4b841e9d43ce/img/asciicast/last_version_openblas.svg")
```

@@

```{r, echo=FALSE}
knitr::include_graphics(path = "https://raw.githubusercontent.com/prdm0/ropenblas/bce920c05f8daa13fc6568e6797d4b841e9d43ce/img/asciicast/rcompiler.svg")
```

@@

```{r, echo=FALSE}
knitr::include_graphics(path = "https://raw.githubusercontent.com/prdm0/ropenblas/bce920c05f8daa13fc6568e6797d4b841e9d43ce/img/asciicast/link_again.svg")
```
